Automated topic naming to support analysis of software maintenance activities

### 2011-01-10 msr/msr2011.tex
f-measures added

\todo[inline]{Topic should be defined clearly (italics and hilighted)}

@@

Topics in software engineering practice refer to specific shared threads of discussions between project stakeholders. 
These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
While addressing a topic of development, stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics are typically latent, i.e., not explicitly named, and can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed)
Within this paper we define \emph{topics} as latent word distributions that describe and compose the documents (version control commits) being analyzed. 
We then defined \emph{labelled topics} as \emph{topics} that have been interpreted and labelled. 
The distinction is important because word distributions can consistent of many words, thus if one has many topics, reading and interpreting these words is prohibitive.
For example, if you read only 10 words per topic from 500 topics you have to read and interpret 5000 words, this is 5 or more pages of text!
Thus \emph{labelled topics} save interpretation time.

@@

Our first word-list set, \textsf{exp1}, was generated using the ontology described in Kayed et al.~\cite{5072519}. 
That paper constructs an ontology for software quality measurement using eighty source documents, including research papers and international standards. 
The labels we used:
\begin{quotation}
\small \noindent \textsf{
integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, reliability.
}
\end{quotation}

@@

\todo[inline]{Should we use F-1 as well to satisfy everyone?}

@@

@@

>>>>

%\todo[inline]{Topic should be defined clearly (italics and hilighted)}

@@

Topics in software engineering practice refer to specific shared threads of discussions between project stakeholders. 
These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
While addressing a topic of development, stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics are typically latent, i.e., not explicitly named, and can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed)
Within this paper we define \emph{topics} as latent word distributions that describe and compose the documents (version control commits) being analyzed. 
We define \emph{labelled topics} as \emph{topics} that have been interpreted and labelled. 
The distinction is important because word distributions can consistent of many words, thus if one has many topics, reading and interpreting these words is prohibitive.
For example, if you read only 10 words per topic from 500 topics you have to read and interpret 5000 words, this is 5 or more pages of text!
Thus \emph{labelled topics} save interpretation time.

@@

Our first word-list set, \textsf{exp1}, was generated using the ontology described in Kayed et al.~\cite{5072519} .
That paper constructs an ontology for software quality measurement using eighty source documents, including research papers and international standards. 
The labels we used:
\begin{quotation}
\small \noindent \textsf{
integrity, security,
interoperability, testability, maintainability, traceability,
accuracy, modifiability, understandability, availability, modularity,
usability, correctness, performance, verifiability, efficiency,
portability, flexibility, reliability.
}
\end{quotation}

@@

%\todo[inline]{Should we use F-1 as well to satisfy everyone?}

@@

% EXP2
For \textsf{exp2}, the average F-measure (macro-F1) for MaxDB was $0.24$ with a range $0.091$ to
$0.37$, and $0.16$ for MySQL with a range of $0$ to $0.41$.
MaxDB had an average precision and recall of $0.25$ and $0.22$
while MySQL had $0.41$ and $0.10$ respectively.

% EXP3
For \textsf{exp3}, the average F-measure (macro-F1) for MaxDB was $0.26$ with a range $0.11$ to
$0.47$, and $0.36$ for MySQL with a range of $0.10$ to $0.65$.
MaxDB had an average precision and recall of $0.16$ and $0.67$
while MySQL had $0.3$ and $0.48$ respectively.

@@

\begin{comment}
maxdb

portability,0.773778920308,0.228070175439,76,12,0.181684100119,0.52,0.14606741573,0.553033707865,288,0.96,13
efficiency,0.832904884319,0.21686746988,36,29,0.124642098177,0.236842105263,0.2,0.557848837209,315,0.915697674419,9
reliability,0.714652956298,0.379888268156,7,104,0.340426350577,0.246376811594,0.829268292683,0.765208858985,244,0.701149425287,34
functionality,0.902313624679,0.0952380952381,32,6,0.0834236909204,0.25,0.0588235294118,0.520961060481,349,0.983098591549,2
maintainability,0.796915167095,0.0919540229885,76,3,0.122505166175,0.571428571429,0.05,0.520145631068,306,0.990291262136,4
usability,0.830334190231,0.175,11,55,0.138109307712,0.112903225806,0.388888888889,0.620320455226,316,0.851752021563,7

total,0.808483290488,0.235897435897,238,209,0.126930463023,0.248201438849,0.224755700326,0.560823829443,1818,0.896891958559,69mysql

portability,0.616040955631,0.137931034483,225,0,0.211497874858,1.0,0.0740740740741,0.537037037037,343,1.0,18
efficiency,0.924914675768,0.3125,33,11,0.297817974114,0.47619047619,0.232558139535,0.606150156324,532,0.979742173112,10
reliability,0.726962457338,0.411764705882,61,99,0.242477699079,0.361290322581,0.478632478632,0.633772529295,370,0.788912579957,56
functionality,0.457337883959,0.0245398773006,315,3,0.00597425429824,0.571428571429,0.012539184953,0.500651614948,264,0.988764044944,4
maintainability,0.686006825939,0,184,0,0,0,0.0,0.5,402,1.0,0
usability,0.919795221843,0.175438596491,27,20,0.13508225345,0.2,0.15625,0.560074458484,534,0.963898916968,5

total,0.721843003413,0.159793814433,845,133,0.0857635592199,0.411504424779,0.0991471215352,0.523778370698,2445,0.9484ahindle@wish:~/projects/lda-paper/src/validate$ cat NOTES 
columns of maxdb.report.text

    out['accuracy'] = acc
    out['f1'] = f1
    out['fn'] = fn
    out['fp'] = fp
    out['mcc'] = mcc
    out['precision'] = pre
    out['recall'] = rec
    out['roca'] = roca
    out['tnr'] = tnr
    out['tn'] = tn
    out['tp'] = tp

cat exp3.*.report.txt 
maxdb

portability,0.706940874036,0.472222222222,38,76,0.286382363909,0.40157480315,0.573033707865,0.659850187266,224,0.746666666667,51
efficiency,0.372750642674,0.222929936306,10,234,0.067549899325,0.130111524164,0.777777777778,0.548772609819,110,0.31976744186,35
reliability,0.434447300771,0.256756756757,3,217,0.195966959965,0.149019607843,0.926829268293,0.651633024951,131,0.376436781609,38
functionality,0.53470437018,0.236286919831,6,175,0.186902353269,0.137931034483,0.823529411765,0.665285832643,180,0.507042253521,28
maintainability,0.627249357326,0.337899543379,43,102,0.111672018872,0.26618705036,0.4625,0.566201456311,207,0.669902912621,37
usability,0.27763496144,0.107936507937,1,280,0.0937953415493,0.0572390572391,0.944444444444,0.594863731656,91,0.245283018868,17

total,0.492287917738,0.257983719474,101,1084,0.0926022435775,0.159689922481,0.671009771987,0.568114654124,943,0.46521953626,206
mysql

portability,0.616040955631,0.412532637076,164,61,0.170139234681,0.564285714286,0.325102880658,0.57363015753,282,0.822157434402,79
efficiency,0.532423208191,0.184523809524,12,262,0.124342460899,0.105802047782,0.720930232558,0.619212814253,281,0.517495395948,31
reliability,0.588737201365,0.404938271605,35,206,0.209194239572,0.284722222222,0.700854700855,0.630811145737,263,0.560767590618,82
functionality,0.622866894198,0.651968503937,112,109,0.240455709256,0.655063291139,0.648902821317,0.620331560471,158,0.591760299625,207
maintainability,0.621160409556,0.218309859155,153,69,-0.00390279540262,0.31,0.16847826087,0.498418234912,333,0.828358208955,31
usability,0.358361774744,0.104761904762,10,366,0.0128981856383,0.0567010309278,0.6875,0.513425090253,188,0.339350180505,22

total,0.556598407281,0.367032074706,486,1073,0.058598680978,0.296393442623,0.481876332623,0.532831106575,1505,0.583785880528,452
\end{comment}
